Microlensing as a possible probe of the internal structure of quasars

### 2015-07-09 paper1/intro.tex

Hundreds of thousands of quasars have been detected up to date, mainly from the Sloan Digital Sky Survey. The great majority of them present a redshift larger than 2.15 of their spectra (\citep{2014A&A...563A..54P}). 
Therefore the typical distance to the objects is in the order of gigaparsecs or above. 
A value that is orders of magnitude larger than the distance to M87. Direct observation of the black hole silhouette of quasars require significant technological advances.
We argue in the present paper that one can probe and study the black hole shadow and its proximal environment belonging to a quasar without having to resolve sub-event horizon scales. 
We consider that this is possible by analyzing the data from microlensing-events. 
Moreover, unlike with the few nearby AGNs, the study of the very large quasar population allows for the statistical refinement of the global properties of AGN by highlighting any particular
characteristic that is present only in Sgr~A* and M87 central region. 
Furthermore, the probing of the event-horizon-scale inner regions of a large number of objects will facilitate the study of the evolution of the previously mentioned region.

>>>>

Hundreds of thousands of quasars have been detected up to date, mainly from the Sloan Digital Sky Survey. The great majority of them present a redshift larger than 2.15 of their spectra (\citep{2014A&A...563A..54P}). 
Therefore the typical distance to the objects is in the order of gigaparsecs or above. 
A value that is orders of magnitude larger than the distance to M87. Direct observation of the black hole silhouette of quasars require significant technological advances.
We argue in the present paper that one can probe and study the black hole shadow and its proximal environment belonging to a quasar without having to resolve sub-event horizon scales. 
We consider that this is possible by analyzing the data from microlensing-events as suggested by Agol and Krolik 1999 (citation). They argue that if the magnification function $\mu_t(p)$ from equation (6) corresponds to a perfect fold then from the function $F(t)$ present in the same equation one can extract the source profile. We argue in the current article that one can partially 
reconstruct the black hole silloute up to a simplified crescent geometry. The crescent fit facillitates an estimation of the black hole mass.       
Moreover, unlike with the few nearby AGNs, the study of the very large quasar population allows for the statistical refinement of the global properties of AGN by highlighting any particular
characteristic that is present only in Sgr~A* and M87 central region. 
Furthermore, the probing of the event-horizon-scale inner regions of a large number of objects will facilitate the study of the evolution of the previously mentioned region.
